### 2018-03-23 Sections/state_of_the_art.tex
tiny

Many experimental methods have been developed for measuring and manipulating individual quantum systems, including single atoms in a cavity, trapped ions, and neutral atoms in an optical lattice. In the atom-cavity system \cite{haroche2006exploring}, the largest Schr{\"o}dinger cat state was created with spin of 25 on a Rydberg atom \cite{facon2016sensitive}. In 2000, Haroche \textit{et al.} generated entanglement among two atoms and a single-photon cavity mode \cite{rauschenbeutel2000step}. Later, entanglement between two photons sequentially emitted by the same single atom in a cavity was demonstrated \cite{wilk2007single}. The entanglement fidelity of 86\% between the two photons was obtained, and importantly, the entanglement-generation efficiency is 15\%, a drastic improvement compared to free-space experiments with single atoms \cite{blinov2004observation}. Individual ions can be trapped in a special electric and/or magnetic fields \cite{leibfried2003quantum}. Multiple trapped ions can be entangled by a laser-induced coupling of the spins \cite{blatt2008entangled}. In the recent year, Blatt \textit{et al.} reported scalable and deterministic generation of multi-ions entanglement, including 8-qubit W state \cite{haffner2005scalable} and 14-qubit GHZ state \cite{monz2011}. An array of cold neutral atoms may be confined in free space by a pattern of crossed laser beams, forming an optical lattice. It is up to 50 qubits for the record of arbitrary coherent addressing of individual neutral atoms in a 3D optical lattice \cite{wang2015coherent}. For two-qubit interaction, several groups reported recently generation and detection of two neural-atom entanglement with single-site-resolved technique \cite{kaufman2015entangling, islam2015measuring, dai2016generation}.

>>>>

Many experimental methods have been developed for measuring and manipulating individual quantum systems, including single atoms in a cavity, trapped ions, and neutral atoms in an optical lattice. In the atom-cavity system \cite{haroche2006exploring}, the largest Schr{\"o}dinger cat state was created with spin of 25 on a Rydberg atom \cite{facon2016sensitive}. In 2000, Haroche \textit{et al.} generated entanglement among two atoms and a single-photon cavity mode \cite{rauschenbeutel2000step}. Later, entanglement between two photons sequentially emitted by the same single atom in a cavity was demonstrated \cite{wilk2007single}. The entanglement fidelity of 86\% between the two photons was obtained, and importantly, the entanglement-generation efficiency is 15\%, a drastic improvement compared to free-space experiments with single atoms \cite{blinov2004observation}. Individual ions can be trapped in a special electric and/or magnetic fields \cite{leibfried2003quantum}. Multiple trapped ions can be entangled by a laser-induced coupling of the spins \cite{blatt2008entangled}. In the recent year, Blatt \textit{et al.} reported scalable and deterministic generation of multi-ions entanglement, including 8-qubit W state \cite{haffner2005scalable} and 14-qubit GHZ state \cite{monz2011}. An array of cold neutral atoms may be confined in free space by a pattern of crossed laser beams, forming an optical lattice. It is up to 50 qubits for the record of arbitrary coherent addressing of individual neutral atoms in a 3D optical lattice \cite{wang2015coherent}. For 2-qubit interaction, several groups reported recently generation and detection of two neural-atom entanglement with single-site-resolved technique \cite{kaufman2015entangling, islam2015measuring, dai2016generation}.
